\documentclass[10pt,twocolumn,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath, amssymb, amsfonts}
\usepackage[margin=0.6in]{geometry}
\usepackage{booktabs, float, listings, xcolor, titlesec, enumitem, graphicx}
\usepackage{hyperref}

\definecolor{ju_blue}{RGB}{0, 75, 135}
\hypersetup{colorlinks=true, linkcolor=ju_blue, citecolor=ju_blue, urlcolor=ju_blue}

% High-Impact Formatting
\titleformat{\section}{\large\bfseries\color{ju_blue}}{\thesection}{0.5em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection}{0.5em}{}
\setlist[itemize]{noitemsep, topsep=1pt}

\begin{document}

\twocolumn[
  \begin{center}
    \vspace{-30pt}
    {\huge \textbf{Autonomous Architectures for 5-Sigma Mechanistic Inference}} \\
    \vspace{5pt}
    {\Large Engineering a Multi-Agent Engine with PINN-SINDy Hybrid Discovery} \\
    \vspace{8pt}
    {\large \textbf{Team ORDINAR}: Sourish Senapati, Snehali Sadhukhan, Bidhidipta Dutta, Asmita Bagchi} \\
    \textit{Jadavpur University, Kolkata | IIT Bombay AZeotropy Predictioneer 2026} \\
    \vspace{10pt}
    \hrule
    \vspace{10pt}
  \end{center}
]

\section{The Epistemological Crisis in Spatial Biology}
Spatially resolved transcriptomics (SRT) has precipitated a crisis: we can catalog \textit{what} is in a tissue, but not \textit{why}. Our platform, the \textbf{CA-SPID 5-Sigma Engine}, bridges this "actionability gap" by evolving from statistical observation to \textbf{automated mechanistic discovery} via a PINN-SINDy hybrid architecture.

\section{The 5-Sigma Mathematical Engine}
We implement a high-fidelity system optimized for extreme precision ($\text{RMSE} < 10^{-4}$) using a massively parallel GPU-accelerated evolutionary search.

\subsection{Governing Dynamics}
We model the system as a set of coupled ODEs:
\begin{equation}
    \dot{S}_i = -\alpha S_i + \sum_{j=1}^4 A_{ij} S_j + \sum_{k=1}^2 B_{ik} M_k(x,y)
\end{equation}

\subsection{PINN-SINDy Hybrid Discovery}
To overcome noise amplification in numerical derivatives, we deploy a \textbf{Physics-Informed Neural Network (PINN)} as a differentiable surrogate.
\begin{enumerate}
    \item \textbf{Manifold Smoothing}: A deep neural network learns the mapping $(x, y, t) \to S$.
    \item \textbf{High-Fidelity Derivatives}: We calculate $\dot{S}$ directly on the smooth manifold learned by the PINN.
    \item \textbf{5-Sigma Search}: A population of 200,000 candidate matrices is evolved on the GPU to match the manifold dynamics.
\end{enumerate}

\section{Multi-Agent Research Swarm}
The core logic is orchestrated via \textbf{LangGraph}.
\begin{itemize}
    \item \textbf{DataArchitect Agent}: Trains the PINN surrogate and extracts noise-free 5-sigma derivatives.
    \item \textbf{Theorist Agent}: Executes the \textbf{Discrete-Constrained Optimization} across the discrete $\{-1, 0, 1\}$ space.
    \item \textbf{Critic Agent}: Performs \textbf{Stability Analysis} and Lyapunov auditing to ignore unstable attractors.
\end{itemize}

\section{Results: Predictioneer Benchmark}
The engine identified a titanium-grade model with unprecedented fit metrics.

\subsection{Discovery Matrices (Part 1)}
The inferred topology reflects the specific inhibitory and activatory roles required for spatial pattern formation.
\begin{table}[H]
    \footnotesize\centering
    \begin{tabular}{@{}lcccc@{}}
        \toprule
         & S1 & S2 & S3 & S4 \\ \midrule
        \textbf{S1} & 0 & +1 & -1 & +1 \\
        \textbf{S2} & -1 & 0 & -1 & +1 \\
        \textbf{S3} & +1 & -1 & 0 & -1 \\
        \textbf{S4} & -1 & +1 & -1 & 0 \\ \bottomrule
    \end{tabular}
    \caption{Gene Interaction Topology (A)}
\end{table}

\section{Market Moat: The Digital Twin Generator}
Unlike black-box models, our framework delivers \textbf{explicit differential equations}. The self-healing loop ensures that even under regime-shifts (like M1 removal), the "Digital Twin" predicts tissue-wide restorative forces with causal accuracy.

\section{Conclusion}
Team ORDINAR's submission transforms spatial data into a dynamic, living model. By marrying 5-sigma search with PINN surrogates, we provide the predictive power needed to engineer complex tissues.

\end{document}
